---
title: "R Notebook"
output: html_notebook
---

Source: https://github.com/ropenscilabs/learngganimate/blob/master/animate.md

All of the `transition_` `ease_` `view_` etc. functions in `gganimate` will build a series of static images. To actually assemble those images into an animation, you will need to call the `animate()` function. This function seems simple, but much like file paths, what seems simple can cause great headaches. `animate()` actually combines many “under the hood” features and video rendering concepts that are not obvious to the majority of R users, but can make the difference between a beautiful smooth animation, and a choppy (or even incorrect) animation.

## Controlling animation speed and quality

```{r}
library(ggplot2)
library(gganimate)

anim <-
  ggplot(mtcars, aes(factor(cyl), mpg)) + 
  geom_boxplot() + 
  transition_states(
    gear,
    transition_length = 3,
    state_length = 1
  ) +
  enter_fade() + 
  exit_shrink() +
  ease_aes('linear')
```

```{r}
anim
```

```{r}
#slow and choppy animation
animate(anim, nframes = 200, fps = 5)
```

## Advanced

```{r}
library(tidyverse)
library(e1071)
library(gganimate)

ntimes <- 20  # how many time points to run the bridge?
nseries <- 10 # how many time series to generate?

# function to generate the brownian bridges
make_bridges <- function(ntimes, nseries) {
  replicate(nseries, c(0,rbridge(frequency = ntimes-1))) %>% as.vector()
}

# construct tibble
tbl <- tibble(
  Time = rep(1:ntimes, nseries),
  Horizontal = make_bridges(ntimes, nseries),
  Vertical = make_bridges(ntimes, nseries),
  Series = gl(nseries, ntimes)
)

base_pic <- tbl %>%
  ggplot(aes(
    x = Horizontal, 
    y = Vertical, 
    colour = Series)) + 
  geom_point(
    show.legend = FALSE,
    size = 5) + 
  coord_equal() + 
  xlim(-2, 2) + 
  ylim(-2, 2) +
  transition_time(time = Time) + 
  shadow_wake(wake_length = 0.2)

animate(base_pic, nframes = 100, fps = 10)
```

## `detail` argument

```{r}
#increase detail
animate(base_pic, nframes = 100, fps = 10, type = "cairo", detail = 3)
```

